---
title: "Analysis of COVID-19 Clinical Trials"
output: html_notebook
---

Using [COVID-19](https://www.kaggle.com/nikhilsingh012/covid19-clinical-trials) dataset.


**[Team]**

| Name    | Description     |
|--       |--               |
| [Steve](https://github.com/steve-lemon)   | .           |


**[Notebook Help]**

- *Cmd+Shift+Enter* to run
- *Cmd+Option+I* to insert code chunk
- *Cmd+Shift+K* to preview in html (no code run)


```{r}
# this is block of code chunk
# plot(cars)
```

--------------------------------------------------------
## Commons {.tabset}

공용 변수와 함수들을 정의함.


### Run Environment

```{r}
# current directory
cat('current-directory =', getwd(), '\n')
# current time in local
cat('current-timestamp =', format(Sys.time(), "%a %b %d %X %Y"), '\n')
```


### ICD 코드 구하기

```{r}
# Fetching ICD Code Information from REST APIs
library(jsonlite)
mySearchICD <- function(code) {
  req <- httr::POST("http://www.koicd.kr/2016/easyFind/search.json",
            httr::add_headers(
              # "Authorization" = paste("Basic", gsub("\n", "", secret)),
              "Content-Type" = "application/x-www-form-urlencoded; charset=UTF-8",
              "Cookie" = "JSESSIONID=B893344D438E4CAE129DAA461AA42771; div_popup=done"
            ),
            body = paste("searchType=01&code1=", code, sep='')
  );
  json <- httr::content(req, as = "text")
  data <- fromJSON(json)
  # print (length(data$list))
  if (length(data$list) <= 0) return(list(code_title='',eng_text='',kor_text=''))
  dd = data$list[,c('code_title', 'eng_text', 'kor_text')]
  return(dd[dd$code_title == code,])
}
# sample for J90
mySearchICD('J90')
```


## 0. Configuration

```{r}
# work and data dir
WORK_DIR = file.path(getwd())
DATA_DIR = file.path(WORK_DIR, 'data' , '')  # to keep the last path-separator.
cat(c('WORK_DIR=', WORK_DIR), '\n', c('DATA_DIR=', DATA_DIR), sep='', append = T)
```


## 1. Main Data Set {.tabset}

Read main data which is origin from [COVID-19](https://www.kaggle.com/nikhilsingh012/covid19-clinical-trials) dataset.


### Diagnoses - Combined

- loading `Diagnoses-Combined200411.csv`

```{r}
DiagCombinedByCountry <- read.table(paste0(DATA_DIR, 'Diagnoses-CombinedByCountry200411.csv'), header = TRUE, sep=',', stringsAsFactors=F)
head(DiagCombinedByCountry)
```

### Diagnoses - CombinedByCountry

- loading `Diagnoses-CombinedByCountry200411.csv`

```{r}
DiagCombined <- read.table(paste0(DATA_DIR, 'Diagnoses-Combined200411.csv'), header = TRUE, sep=',', stringsAsFactors=F)
head(DiagCombined)
```


## 2. Pre-Processing



## 3. Pre-Processing











