---
title: "Analysis of COVID-19 Clinical Trials"
output: html_notebook
---

Using [COVID-19](https://www.kaggle.com/nikhilsingh012/covid19-clinical-trials) dataset.


**[Team]**

| Name    | Description     |
|--       |--               |
| [Steve](https://github.com/steve-lemon)   | .           |


**[Notebook Help]**

- *Cmd+Shift+Enter* to run
- *Cmd+Option+I* to insert code chunk
- *Cmd+Shift+K* to preview in html (no code run)


```{r}
# this is block of code chunk
# plot(cars)
```

--------------------------------------------------------
## Commons {.tabset}

공용 변수와 함수들을 정의함.


### Run Environment

```{r}
# current directory
cat('current-directory =', getwd(), '\n')
# current time in local
cat('current-timestamp =', format(Sys.time(), "%a %b %d %X %Y"), '\n')
```


### ICD 코드 구하기

```{r}
# Fetching ICD Code Information from REST APIs
library(jsonlite)
mySearchICD <- function(code, all=T) {
  req <- httr::POST("http://www.koicd.kr/2016/easyFind/search.json",
            httr::add_headers(
              # "Authorization" = paste("Basic", gsub("\n", "", secret)),
              "Content-Type" = "application/x-www-form-urlencoded; charset=UTF-8",
              "Cookie" = "JSESSIONID=B893344D438E4CAE129DAA461AA42771; div_popup=done"
            ),
            body = paste("searchType=01&code1=", code, sep='')
  );
  json <- httr::content(req, as = "text")
  data <- fromJSON(json)
  # print (length(data$list))
  if (length(data$list) <= 0) return(list(code_title='',eng_text='',kor_text=''))
  dd = data$list[,c('code_title', 'eng_text', 'kor_text')]
  if (all) return(dd)
  return(dd[dd$code_title == code,])
}
# sample for J20
mySearchICD('J20')
```


### ICD 코드 정규화

```{r}
# get Major Code of ICD
myMajorICD <- function(x='J20.1'){
  # install.packages("stringr")
  library(stringr)
  Y = str_match(x,'^([A-Z][0-9]{2,})\\.?[0-9]*$')
  return(Y[,2])
}
assertthat::are_equal(myNormICD('J20.1'), 'J20')
stopifnot(myMajorICD('J20.1') == 'J20')
stopifnot(is.na(myMajorICD('JJ20')))
stopifnot(is.na(myMajorICD('')))
```
 


## 0. Configuration

```{r}
# work and data dir
WORK_DIR = file.path(getwd())
DATA_DIR = file.path(WORK_DIR, 'data' , '')  # to keep the last path-separator.
cat(c('WORK_DIR=', WORK_DIR), '\n', c('DATA_DIR=', DATA_DIR), sep='', append = T)
```


## 1. Main Data Set {.tabset}

Read main data which is origin from [COVID-19](https://www.kaggle.com/nikhilsingh012/covid19-clinical-trials) dataset.


### Diagnoses - Combined

- loading `Diagnoses-Combined200411.csv`

```{r}
DiagCombinedByCountry <- read.table(paste0(DATA_DIR, 'Diagnoses-CombinedByCountry200411.csv'), header = TRUE, sep=',', stringsAsFactors=F)
head(DiagCombinedByCountry)
```

### Diagnoses - CombinedByCountry

- loading `Diagnoses-CombinedByCountry200411.csv`

```{r}
DiagCombined <- read.table(paste0(DATA_DIR, 'Diagnoses-Combined200411.csv'), header = TRUE, sep=',', stringsAsFactors=F)
head(DiagCombined)
```


## 2. Pre-Processing {.tabset}

Manipulating Origin Data

### ICD Code Table

```{r}
DiagCombined[,c('icd_code','icd_version')]
# combine two data
myIcdTable = merge(DiagCombined[,c('icd_code','icd_version')], DiagCombinedByCountry[,c('icd_code','icd_version')])
head(myIcdTable[20:30,])
```


### ICD Lookup Set

```{r}
# load LookUp Table by CODE -> TEXT{ENG, KOR}
myLoadIcdLUT <- function(max_nrow=5){
  MY_FILE = 'my-icd-lookup.cached.csv'
  # STEP.0 `my-icd-lookup.cached.csv` 파일이 있으면 무시.
  f <- list.files(DATA_DIR, MY_FILE)
  if (length(f) > 0){
    dt <- read.table(paste0(DATA_DIR, MY_FILE), header = T, sep=',', stringsAsFactors=F)
    return(dt)
  }

  #dplyr 패키지 for distinct(데이터, 컬럼)
  library(dplyr)
  # STEP.1 icd_code 중복 걸려냄
  myIcdLUT <- distinct(myIcdTable)
  cols <- colnames(myIcdLUT)
  cat('cols =', cols, '\n')

  # add columns of characters...
  my2 <- cbind(myIcdLUT, list(eng_text = '', kor_text = ''))
  my2 <- transform(my2, eng_text = as.character(eng_text), kor_text = as.character(kor_text))  # to character.

  # STEP.2 pre-processing to detect major ICD code ('J20.10' -> 'J20')
  process_row = function(row){
    row = row[1,]
    row[['mjr_code']] = myMajorICD(row[['icd_code']])
    return(row)
  }
  # STEP.2-1 using lapply
  my3 <- lapply(1:nrow(my2), function(r_num) { process_row(my2[r_num, ]) })
  my4 <- do.call(rbind, my3)
  #str(my4)                          # 3624 obs. of  5 variables: icd_code, icd_version, eng_text, kor_text, mjr_code

  # STEP.2-2 get unique list of major-code
  my5 = distinct(my4, mjr_code)
  str(my5)                          # 985 obs. of  1 variable: mjr_code

  # STEP.3 fetch and stack up code list
  my5_len = ifelse(max_nrow > 0, max_nrow, nrow(my5))
  my6 <- vector(mode = "list", length = my5_len)
  process_my5 <- function(mjr_code){
    # print(mjr_code)
    if (is.na(mjr_code)) return(data.frame(code_title=c(),eng_text=c(),kor_text=c()))
    # res <- data.frame(code_title=c('Z99', mjr_code),eng_text=c('ZZZZ', '.'),kor_text=c('9999', 'z'))  # as dummy data
    res <- mySearchICD(mjr_code)
    Sys.sleep(2)
    return(res)
  }
  for(row_x in 1:my5_len){
    mjr_code = my5[row_x, 'mjr_code']
    row_y <- process_my5(mjr_code)
    my6[[row_x]] <- row_y
  }
  my7 <- do.call(rbind, my6)

  # STEP.4 save into cached file.
  write.csv(my7, file = paste0(DATA_DIR, MY_FILE), row.names = FALSE)
  
  # FINAL. returns
  ret <- my7
  return(ret)
}
# load ICD-LUT table
myLoadIcdLUT(max_nrow = 0)
```


### Embedding Names




## 3. Processing











