---
title: "Analysis of COVID-19 Clinical Trials"
output: html_notebook
---

Using [COVID-19](https://www.kaggle.com/nikhilsingh012/covid19-clinical-trials) dataset.


**[Team]**

| Name    | Description     |
|--       |--               |
| [Steve](https://github.com/steve-lemon)   | .           |


**[Notebook Help]**

- *Cmd+Shift+Enter* to run
- *Cmd+Option+I* to insert code chunk
- *Cmd+Shift+K* to preview in html (no code run)


```{r}
#! below are the required packages.
# install.packages("curl")
# install.packages("httr")
# install.packages('assertthat')
# install.packages('dplyr')
```

--------------------------------------------------------
## Commons {.tabset}

공용 변수와 함수들을 정의함.


### Run Environment

```{r}
# current directory
cat('current-directory =', getwd(), '\n')
# current time in local
cat('current-timestamp =', format(Sys.time(), "%a %b %d %X %Y"), '\n')
```


### ICD 코드 구하기

```{r}
# Fetching ICD Code Information from REST APIs
library(jsonlite)
mySearchICD <- function(code, all=T) {
  req <- httr::POST("http://www.koicd.kr/2016/easyFind/search.json",
            httr::add_headers(
              # "Authorization" = paste("Basic", gsub("\n", "", secret)),
              "Content-Type" = "application/x-www-form-urlencoded; charset=UTF-8",
              "Cookie" = "JSESSIONID=B893344D438E4CAE129DAA461AA42771; div_popup=done"
            ),
            body = paste("searchType=01&code1=", code, sep='')
  );
  json <- httr::content(req, as = "text")
  data <- fromJSON(json)
  # print (length(data$list))
  if (length(data$list) <= 0) return(list(code_title='',eng_text='',kor_text=''))
  dd = data$list[,c('code_title', 'eng_text', 'kor_text')]
  if (all) return(dd)
  return(dd[dd$code_title == code,])
}
# sample for J20
mySearchICD('J20')
```

### ICD 분류처리(대/중/소) 

- ICD Code classification 2020 06 08 CSM
- TESTING commit to github

```{r}
loadICDCodeFromWeb <- function(code, all=T) {
  req <- httr::POST("http://www.koicd.kr/2016/easyFind/search.json",
            httr::add_headers(
              # "Authorization" = paste("Basic", gsub("\n", "", secret)),
              "Content-Type" = "application/x-www-form-urlencoded; charset=UTF-8",
              "Cookie" = "JSESSIONID=B893344D438E4CAE129DAA461AA42771; div_popup=done"
            ),
            body = paste("searchType=01&code1=", code, sep='')
  );
  json <- httr::content(req, as = "text")
  data <- fromJSON(json)
  # print (length(data$list))
  if (length(data$list) <= 0) return(list(code_title='',eng_text='',kor_text=''))
  dd = data$list[,c('code_title', 'eng_text', 'kor_text')]
  if (all) return(dd)
  return(dd[dd$code_title == code,])
}

# sample for J20
loadICDCodeFromWeb('J20')
```

### ICD 코드 정규화

```{r}
# get Major Code of ICD
myMajorICD <- function(x='J20.1'){
  # install.packages("stringr")
  library(stringr)
  Y = str_match(x,'^([A-Z][0-9]{2,})\\.?[0-9]*$')
  return(Y[,2])
}
assertthat::are_equal(myNormICD('J20.1'), 'J20')
stopifnot(myMajorICD('J20.1') == 'J20')
stopifnot(is.na(myMajorICD('JJ20')))
stopifnot(is.na(myMajorICD('')))
```
 

### BioBERT NERs

- using [BERN](https://bern.korea.ac.kr/) based on ([BioBERT (Lee et al., 2019)](https://arxiv.org/abs/1901.08746))

```{r}
#! search NER(Named Entity Recognition) via Neural BioBERT Service
mySearchNER <- function(txt, dummy=F) {
  # load dummy for test
  if (dummy){
    json = "{\"project\":\"BERN\",\"sourcedb\":\"\",\"sourceid\":\"b39dba2f6744bb5cf68cf8d0137e11c1c3dc5f57e1cd38611f4a4b3b\",\"text\":\"Acute respiratory failure, type II [hypercapnic]\",\"denotations\":[{\"id\":[\"MESH:D000208\",\"BERN:259462001\"],\"span\":{\"begin\":0,\"end\":5},\"obj\":\"disease\"},{\"id\":[\"MESH:D012131\",\"BERN:106908201\"],\"span\":{\"begin\":6,\"end\":25},\"obj\":\"disease\"}],\"timestamp\":\"Tue Jun 16 14:32:57 +0000 2020\",\"logits\":{\"disease\":[[{\"start\":0,\"end\":5,\"id\":\"MESH:D000208\\tBERN:259462001\"},0.962023913860321],[{\"start\":6,\"end\":25,\"id\":\"MESH:D012131\\tBERN:106908201\"},0.9626538753509521]],\"gene\":[],\"drug\":[],\"species\":[]}}"
    data <- fromJSON(json)
    return(data)
  }

  # "https://bern.korea.ac.kr/senddata",
  httr::set_config(httr::config(ssl_verifypeer = 0L))
  req <- httr::POST('https://bern.korea.ac.kr/plain',
            httr::add_headers(
              "Content-Type" = "application/x-www-form-urlencoded; charset=UTF-8",
              "Cookie" = "connect.sid=s%3ANPqwNBa_UTo2leh20iJLS0GJjzLA_f6e.yn1Dj3SEJ4mQqWEu2IXw8hYYPue6PHwknzqfsGShPwc"
            ),
            body = list("sample_text" = txt, "req_type" = "text"),
            encode = 'form'
  )
  json <- httr::content(req, as = "text")
  print(json)
  data <- fromJSON(json)
  return(data)
}
#mySearchNER('Acute respiratory failure, type II [hypercapnic]', dummy = T)

#! detect list of NER
myParseNER <- function(txt, dummy=F) {
  data = mySearchNER(txt, dummy)
  txt = data$text
  ret = list()
  # print(txt)
  for(d in data$logits$disease){
    # print(paste0(list(d[[1]]$start, d[[1]]$end), '-'))
    dis = tolower(substr(txt, d[[1]]$start+1, d[[1]]$end))
    ret <- append(ret, dis)
  }
  return(ret)
}

#! test case with dummy.
dum1 = myParseNER('Acute respiratory failure, type II [hypercapnic]', dummy = T)
assertthat::are_equal(dum1[[1]], 'acute')
assertthat::are_equal(dum1[[2]], 'respiratory failure')
```

### ICD Text


```{r}
#! fetch the icd text with table
myFetchICDTextByTable <- function(icd_table, max_nrow=0){
  #dplyr 패키지 for distinct(데이터, 컬럼)
  library(dplyr)
  # STEP.1 icd_code 중복 걸려냄
  myIcdLUT <- distinct(icd_table)
  cols <- colnames(myIcdLUT)
  cat('cols =', cols, '\n')

  # add columns of characters...
  my2 <- cbind(myIcdLUT, list(eng_text = '', kor_text = ''))
  my2 <- transform(my2, eng_text = as.character(eng_text), kor_text = as.character(kor_text))  # to character.

  # STEP.2 pre-processing to detect major ICD code ('J20.10' -> 'J20')
  process_row = function(row){
    row = row[1,]
    row[['mjr_code']] = myMajorICD(row[['icd_code']])
    return(row)
  }
  # STEP.2-1 using lapply
  my3 <- lapply(1:nrow(my2), function(r_num) { process_row(my2[r_num, ]) })
  my4 <- do.call(rbind, my3)
  #str(my4)                          # 3624 obs. of  5 variables: icd_code, icd_version, eng_text, kor_text, mjr_code

  # STEP.2-2 get unique list of major-code
  my5 = distinct(my4, mjr_code)
  str(my5)                          # 985 obs. of  1 variable: mjr_code

  # STEP.3 fetch and stack up code list
  my5_len = ifelse(max_nrow > 0, max_nrow, nrow(my5))
  my6 <- vector(mode = "list", length = my5_len)
  process_my5 <- function(mjr_code){
    # print(mjr_code)
    if (is.na(mjr_code)) return(data.frame(code_title=c(),eng_text=c(),kor_text=c()))
    # res <- data.frame(code_title=c('Z99', mjr_code),eng_text=c('ZZZZ', '.'),kor_text=c('9999', 'z'))  # as dummy data
    res <- mySearchICD(mjr_code)
    Sys.sleep(2)
    return(res)
  }
  for(row_x in 1:my5_len){
    mjr_code = my5[row_x, 'mjr_code']
    row_y <- process_my5(mjr_code)
    my6[[row_x]] <- row_y
  }
  my7 <- do.call(rbind, my6)
  return(my7)  
}
#myFetchICDTextByTable(list())
dd1 = data.frame(list('icd_code'='J20', 'icd_version'=10), stringsAsFactors = FALSE)
dd1[nrow(dd1) + 1,] = list('icd_code'='J20.1', 'icd_version'=10)
dd1[nrow(dd1) + 1,] = list('icd_code'='J20', 'icd_version'=10)
myFetchICDTextByTable(dd, max_nrow = 1)
```


### Load/Save CSV

```{r}
#! save dataframe to csv file.
mySaveToCSV <- function(df, name, dir = DATA_DIR, safe = F){
  # STEP.0 check if file exists..
  f <- list.files(dir, name)
  if (safe && length(f) > 0){
    fname <- paste0(dir, name)
    cat('load via file:', fname, '\n')
    dt <- read.table(fname, header = T, sep=',', stringsAsFactors=F)
    return(dt)
  }
  ret = write.csv(df, file = paste0(dir, name), row.names = FALSE)
  return(ret)
}
```



## 0. Configuration

```{r}
# work and data dir
WORK_DIR = file.path(getwd())
DATA_DIR = file.path(WORK_DIR, 'data' , '')  # to keep the last path-separator.
cat(c('WORK_DIR=', WORK_DIR), '\n', c('DATA_DIR=', DATA_DIR), sep='', append = T)
```


## 1. Main Data Set {.tabset}

Read main data which is origin from [COVID-19](https://www.kaggle.com/nikhilsingh012/covid19-clinical-trials) dataset.


### Diagnoses - Combined

- loading `Diagnoses-Combined200411.csv`

```{r}
DiagCombinedByCountry <- read.table(paste0(DATA_DIR, 'Diagnoses-CombinedByCountry200411.csv'), header = TRUE, sep=',', stringsAsFactors=F)
head(DiagCombinedByCountry)
```

### Diagnoses - CombinedByCountry

- loading `Diagnoses-CombinedByCountry200411.csv`

```{r}
DiagCombined <- read.table(paste0(DATA_DIR, 'Diagnoses-Combined200411.csv'), header = TRUE, sep=',', stringsAsFactors=F)
head(DiagCombined)
```


## 2. Pre-Processing {.tabset}

Manipulating Origin Data


### ICD Code Table

```{r}
DiagCombined[,c('icd_code','icd_version')]
# combine two data
myIcdTable <- merge(DiagCombined[,c('icd_code','icd_version')], DiagCombinedByCountry[,c('icd_code','icd_version')])
head(myIcdTable[20:30,])
```


### ICD Lookup Set

```{r}
# load LookUp Table by CODE -> TEXT{ENG, KOR}
myLoadIcdLUT <- function(table, max_nrow=5){
  MY_FILE = 'my-icd-lookup.cached.csv'
  # STEP.0 `my-icd-lookup.cached.csv` 파일이 있으면 무시.
  f <- list.files(DATA_DIR, MY_FILE)
  if (length(f) > 0){
    dt <- read.table(paste0(DATA_DIR, MY_FILE), header = T, sep=',', stringsAsFactors=F)
    return(dt)
  }

  # STEP.2 fetch search-list, and save as cached.
  ret <- myFetchICDTextByTable(table, max_nrow)
  write.csv(ret, file = paste0(DATA_DIR, MY_FILE), row.names = FALSE)
  
  # FINAL. returns
  return(ret)
}

# load ICD-LUT table (cols='code_title', 'eng_text', 'kor_text')
myIcdLUT <- myLoadIcdLUT(myIcdTable, max_nrow = 0)
head(myIcdLUT[20:30,])
```


### Embedding ICD Names

- add `eng_text`, `kor_text` by `icd_code`.

```{r}
#! only if num_patients > 0
data = DiagCombined[DiagCombined$num_patients > 0, c('icd_code', 'num_patients')]
assertthat::are_equal(colnames(data), c('icd_code', 'num_patients'))

# find eng and kor
my_find_text_by_code <- function(code){
  f = myIcdLUT[myIcdLUT$code_title == code,]
  r = list('eng' = '', 'kor' = '', 'icd' = code)
  if (nrow(f) > 0){
    r$eng = f$eng_text[1]
    r$kor = f$kor_text[1]
  }
  return(r)
}
dm2 = my_find_text_by_code('A04.4')
assertthat::are_equal(dm2$icd, 'A04.4')
assertthat::are_equal(dm2$eng, 'Other intestinal Escherichia coli infection')
assertthat::are_equal(dm2$kor, '기타 장대장균감염')

#! merge 'icd_code' and 'eng_text'
myMergeICDText <- function(df, use_major = T){
  # STEP.1 add columns
  my2 <- cbind(df, list(icd_eng = '', icd_kor = ''))
  if(use_major){
    my2 <- cbind(df, list(mjr_code = '', mjr_eng='', mjr_kor=''))
  }
  process_row <- function(row){
    row = row[1,]
    txt = my_find_text_by_code(row[['icd_code']])
    row[['icd_eng']] = txt$eng
    row[['icd_kor']] = txt$kor
    if (use_major) {
      row[['mjr_code']] = myMajorICD(row[['icd_code']])
      txt = my_find_text_by_code(row[['mjr_code']])
      row[['mjr_eng']] = txt$eng
      row[['mjr_kor']] = txt$kor
    }
    return(row)
  }
  # STEP.2 process each rows
  my3 <- lapply(1:nrow(my2), function(r_num) { process_row(my2[r_num, ]) })
  my4 <- do.call(rbind, my3)
  return(my4)
}

#! split icd_code -> 'major' & 'code'
DiagPatients <- myMergeICDText(data)
head(DiagPatients)
```


### Group by Major ICD

- sub-sum patients by major icd-code.


```{r}
#! group by column
my_group_by_mjr_code <- function(df){
  #library(dplyr)
  #ret <- df %>% group_by(mjr_code) %>% summarise(num_patients = sum(num_patients))
  #return(ret)
  df2 <- aggregate(num_patients ~ mjr_code, df, sum)
  return(df2)
}

#! store
data = my_group_by_mjr_code(DiagPatients)
assertthat::are_equal(data[data$mjr_code == 'A09', c('num_patients')], 19+13)  # 32 = 19(A09.9) + 13(A09.0)
colnames(data) = c('icd_code', 'sum')
DiagMajorICD <- myMergeICDText(data, use_major = F)
#! load (or save to file)
DiagMajorICD <- mySaveToCSV(DiagMajorICD, 'my-icd-major-patients.csv', safe = T)
# show table
DiagMajorICD
```


## 3. Processing











